Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2012-04-25 extended_catalog/paper/extended_search.tex
updated test

\newtext{
These simulations spanned the range of detectable fluxes 
over two different energy ranges, but only assuming an isotropic background.
We performed a second simulation to assess any effects that could
be introduces by performing this test in the presence of a highly
structured background.
Our simulation setup was the same as above except that the sources
were simulated on top of and analyzed assuming the presence of
the standard Galactic and isotropic diffuse background model used
in 2FGL.

In our simulation, we selected our sources to have a random position on the sky
such that the absolute value of the galactic latitude of the source is
less than 5\degree, probing the most structured areas of the galaxy.

To limit the number of tests, we selected only one flux
level for each of the four spectral indices and we perform
this test only in the 1 \gev to 100 \gev energy range. 
The source flux was selected so that $\ts\sim50$. This is around 
the significance level for which on might
expect to be able to spatially resolve the source. 
We do not test brighter sources since the structured background
should produce the most significant effect for very bright sources.

Because the Galactic diffuse emission is highly structure, the point-source
sensitivity can vary significantly across the galactic plane.
To account for this, we scaled the flux (for a given spectral index)
so that the source always has approximatly the same signal-to-noise ratio:
\begin{equation}
  \label{scale_flux_by_background}
  F(\vec{x}) = F(\text{GC}) \times \left(
  \frac{B(\vec{x})}{B(\text{GC})}\right)^{1/2}.
\end{equation}
Here, $\vec{x}$ is the position of the source, $F$ is the integral
flux of the simulated source from 100 \mev to 100 \gev, $F(\text{GC})$
is the same quantity if the source were at the galactic center, $B$
is the integral of the Galactic diffuse and isotropic diffuse emission
model from 1 \gev to 100 \gev and $B(\text{GC})$ is the same quantity
if the source were at the galactic center.  Table~\ref{ts_ext_num_sims}
tabulates $F(\text{GC})$ and the average \ts for the four spectral models.
For each spectral index, we performed $\sim90,000$ simulations.

Figure~\ref{tsext_plane_plot} shows the cumulative density
of \tsext compared to the $\chi^2_1/2$ distribution of
Equation~\ref{ts_ext_distribution}. For small values of \tsext,
there is reasonable agreement between the Monte Carlo simulation and
theory.  At the highest obtained values of \tsext, there is possibly
some discrepancy.  But in this range there are only limited statistics
because the curve is determined by only a few points.

\subsection{\newtext{Assessing the Bias Due to Incorrect Spatial Models}}
\label{bias_wrong_spatial_model}

\newtext{
We performed a Monte Carlo study to asses the biases introduced by incorrectly
modeling the spatial structure of an extended source. This is important because any assumed spatial
model is just an approximation to the true photon distribution of the source.

To assess this systematic, we simulated the spatially extended ring-type SNR W44.
W44 was selected because it is the most significant extended source detected by the LAT 
that has been reported as having a non-radially symmetric photon-distribution \cite{w44}.

W44 was simulated with a power-law spectral model. The flux and spectral index of this source
were taken from our re-analysis in this paper which is described in Section~\ref{validate_known}
and summarized in Table~\ref{known_extended_sources}. In particular W44 was simulated
with a flux of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100 \gev with a spectral
index of 2.66.

W44 was simulated with an elliptical ring spatial model described in
\cite{w44}.  Because that publication does not provide the numbers describing
the parameters of the ellipse, we summarize them here for completeness. The elliptical
spatial model has a major axis of 0\fdg3 and a minor axis of 0\fdg19. The
ellipse predicts emission only for the outer 0.75\% of the ellipse and
the ellipse has an angle of $147\degree$ measured east of celestial north.

We used a simulation setup similar to that described in
Section~\ref{monte_carlo_validation}, but the source was simulated on
top of and analyzed assuming the presence of the standard galactic and
isotropic diffuse background model used in 2FGL.  This simulation was
in the 1 \gev to 100 \gev energy range and
the sources were simulated over the two-year time range included in the
2FGL catalog. We performed 985 identical simulations with different seeds to
see the statistical spread in the fit values.
In the simulations of W44, we disabled the inherent energy dispersion of photons
by the LAT. The bias caused by ignoring energy dispersion 
will be discussed in an upcoming paper by the LAT collaboration \citep{lat_on_orbit_psf}.

After simulating the ring-like source, we fit the spectral and spatial parameters of 
the ring-like extended source with successively more complicated spatial models.
We obtained the best fit spatial parameters using \pointlike and, using 
these best fit spatial parameters, obtained the best fit spectral parameters 
using \gtlike. In total, we performed the fit using a point-like spatial model,
using a radially-symmetric uniform Gaussian and disk spatial model, 
an Elliptical disk spatial model, and finally the Monte Carlo true Elliptical
ring spatial model.

Figure~\ref{ts_comparison_w44sim} shows the distribution of TS values for 
each of the simulations when fitting the simulated sources 
with the different spatial models. 
Figure~\ref{ts_comparison_w44sim}a shows the distribution of \ts values when 
fitting the simulated Elliptical ring extended source as as a point-like source.
the source is very significant as a point source ($\ts\sim3500$).
Figure~\ref{ts_comparison_w44sim}b shows the distirbution of \tsext values
when fitting the source as a radially-symmetric uniform disk or Gaussian source.
The source is very significiantly extended ($\tsext\sim250$). 
On average \tsext is slightly larger when
fitting the source with the Disk spatial model compared to the Gaussian spatial model.
Considering that the simulated source's true spatial model has a sharp edge, it
makes sense that the Disk would provide a better fit.

Figure~\ref{ts_comparison_w44sim}c then shows the change in \ts (or
twice the improvement in log likelihood) when fitting the simulated source as
an elliptical disk compared to fitting the source as a disk. Since the change
in \ts is $\sim30$, we see that our simulated source is significantly better
described with an ellpitical spatial model. Finally, 
Figure~\ref{ts_comparison_w44sim}d shows the change in \ts when fitting
the source as an elliptical ring compared to fitting it as an elliptical disk.
Since the change is $\sim9$, we see that the source is somewhat better described
by the true spatial model, but not at a high statistical significance.

Figure~\ref{bias_w44sim} shows the distirbution of best fit parameters
for these simulations. Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b
show the distribututions of best fit flux and spectral indices.
They show that when fitting this simulated extended source with a point-like
spatial model, there is a $\sim$10\% bias in the fit flux and
$\sim5\%$ bias in the fit index. But when fitting the sources with any of
the extended spatial models, there is no bias in the best fit spectral parameters
(within the precision of this Monte Carlo study. The reason for this is
because within the finite angular precision and limited statistics of the LAT, 
all of the extended spatial models can be adjusted to look almost the same.
For brighter or larger sources, this could potentially be a larger effect.

Figure~\ref{bias_w44sim}c plots the best fit 68\% containment radius
(\rsixeight).  For the elliptical ring spatial model, as expected
there is no significant bias in the best fit size. What is surprising
is that for none of the tested spatial models was the bias greater
than $\sim10\%$. This shows that for whatever spatial model is used,
the best fit \rsixeight is a reasonable measure of the true 68\%
containment radius.

For completeness, for the elliptical disk and ring spatial models,
Figure~\ref{bias_w44sim}c plots the distribution of best fit eccentricity
of the ellipse. It is defined as $\sqrt{1-b^2/a^2}$ where $a$ is the
length of the semi-major axis and $b$ is the length of the semi-minor
axis.  Figure~\ref{bias_w44sim}c plots the distribution of best fit
orientation angle of the ellipse. For the elliptical spatial models,
there is no systematic bias in the eccentricities or orentiation angles.
For the true sptial model, there is less spread in the distributions of
the fit parameters.  Finally, for completeness Figure~\ref{bias_w44sim}d
shows that the distirubtion of best fit ring fractions is unbiased when
the source is fit with the for the elliptical ring spatial model.

@@

\newtext{
It might be desirable to formulate a Bayesian test comparing an extended
source to two point-like sources.
We considered the Bayesian information criterion \citep[BIC,][]{BIC_statistical_test}. 
We found it difficult
to apply to LAT data because it required a term including the number of data points
and for LAT events, there are many photons included in the ROI that contribute only
 marginally when considering different models.
We also considered the Akaike information criterion \citep[\aic,][]{AIC_statistical_test}.
The \aic is defines as
\begin{equation}
  \aic=2k-2\log\likelihood
\end{equation}
where $k$ is the number of parameters in the model. 
The first term in the \aic penaize models with additonal parameters. 
In this formulation, the best model is consided to be the one that minimzies the \aic.
Because the two point-like source hypotheses has
three more parameters compared to the one extended source hypothesis (two spatial
parameters and two spectral parameters compared to one extnesion parameter),
we note that the $\tsext>\tsinc$ is mathematically equivalent to the test that
\begin{equation}
  \aic_\text{ext} < \aic_\text{2pts} - 6,
\end{equation}
which gives our original test an equivalent Bayesian formulation by requring 
$\aic_\text{ext}$ to be sufficently smaller than $\aic_\text{2pts}$.
}

@@

For each candidate that was not biased by neighboring point-like
sources or by large-scale residuals in the diffuse emission model, we
improved the model of the region by deciding on a case by case basis which
background point-like sources should be kept.  We kept in our model the
sources that we
believed represented physically distinct sources and we removed 
sources that we believed were included in the 2FGL catalog to compensate
for residuals induced by not modeling the extension of the source.
Soft nearby point-like 2FGL sources that were not significant at higher energies
were frozen to the spectras predicted by 2FGL.
When deciding
which background sources to keep and which to remove, we used as much as possible
multiwavelength information about possibly extended source counterparts
to help guide our choice. For each extended source presented in 
Section~\ref{new_ext_srcs_section}, we describe any modifications from 2FGL
of the background model that were performed.
\newtext{In Table~\ref{fake_2fgl_sources}, we will summarize the sources that were 
included in 2FGL to account for residuals induced by not modeling the extension of
a nearby source.}

@@

Nine extended sources not included in the 2FGL catalog were found by our
extended source search. Two of these have been previously
studied in dedicated publications: RX\,J1713.7$-$3946 and Vela
Jr. \citep{rx_j1713_lat,vela_jr_lat}.
Two of these sources were
found when using photons with energies between 1 \gev and 100 \gev and seven
were found when using photons with energies between 10 \gev and 100 \gev.
For the sources found at energies above 10 \gev, we restrict our
analysis to higher energies because of the issues
of source confusion and diffuse emission modeling described in
Section~\ref{extended_source_search_method}.
The spectral and spatial properties of these nine sources are summarized
in Table~\ref{new_ext_srcs_table} and the results of our investigation of
systematic errors are presented in Table~\ref{alt_diff_model_results}.
Table~\ref{alt_diff_model_results}
also
compares the likelihood assuming the source is spatially
extended to the likelihood assuming 
that the emission originates from two independent point-like
sources. For these new extended sources, $\tsext>\tsinc$ 
so we conclude that 
the \gev emission does not originate from two physically
distinct point-like sources (see Section~\ref{dual_localization_method}).  
Table~\ref{alt_diff_model_results} also includes the
results of the extension fits using variations of the PSF and the Galactic
diffuse model described in Section~\ref{systematic_errors_on_extension}.
There is good agreement between \tsext and the fit size using the standard
analysis, the alternative approach to modeling the diffuse emission, and the alternative PSF.
This suggests that the sources are robust against mis-modeled features in the diffuse
emission model and uncertainties in the PSF.
\newtext{Finally, in Table~\ref{fake_2fgl_sources} we 
summarize the sources included in 2FGL to account for residuals induced
by not modeling the extension of a nearby source.}

@@

2FGL\,J1837.3$-$0700c was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the \tev source HESS\,J1837$-$069.  This source is
in a complicated region.  Figure~\ref{1FGL_J1837.5-0659c}a shows a
smoothed counts map of the region and overlays the \tev contours of
HESS\,J1837$-$069 \citep{hess_plane_survey}.  There are two very nearby
point-like 2FGL sources, 2FGL\,J1836.8$-$0623c and 2FGL\,J1839.3$-$0558c,
that clearly represent distinct sources.  On the other hand, there is
another source 2FGL\,J1835.5$-$0649 located between the three sources that
appears to correlate with the \tev morphology of HESS\,J1837$-$069 but
at \gev energies
does not appear to represent a physically distinct source.  We concluded
that this source was included in the 2FGL catalog to compensate for residuals induced by
not modeling the extension of this source and removed it from our model
of the sky.  Figure~\ref{1FGL_J1837.5-0659c}b shows a
counts map of this region after subtracting these background sources.
After removing 2FGL\,J1835.5$-$0649,
we tested for
source confusion by fitting 
2FGL\,J1837.3$-$0700c
instead as two point-like sources.
\newtext{Because $\tsinc=10.8$ is less than $\tsext=18.5$, we conclude that this emission
does not originate from two nearby point-like sources.

With this model, 2FGL\,J1837.3$-$0700c was found to have an
extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$.}
While fitting the extension of 2FGL\,J1837.3$-$0700c,
we iteratively relocalized the two closest
background sources along with the extension of 2FGL\,J1837.3$-$0700c but
their positions did not significantly change.  2FGL\,J1834.7$-$0705c
moved to $(l,b)=(24\fdg77,0\fdg50)$, 2FGL\,J1836.8$-$0623c moved
to $(l,b)=(25\fdg57,0\fdg32)$.

@@

\startdata
\multicolumn{6}{c}{Isotropic Background} \\
\hline
      1.5 &  $3\times 10^{-7}$ &           18938 &  22233    &     18938   &    8084     \\
          &          $10^{-7}$ &           19079 &   5827    &     19079   &    2258     \\
          &  $3\times 10^{-8}$ &           19303 &   1276    &     19303   &     541     \\
          &          $10^{-8}$ &           19385 &    303    &     19381   &     142     \\
          &  $3\times 10^{-9}$ &           18694 &     62    &     12442   &      43     \\
      \hline
        2 &          $10^{-6}$ &           18760 &  22101    &     18760   &    3033     \\
          &  $3\times 10^{-7}$ &           18775 &   4913    &     18775   &     730     \\
          &          $10^{-7}$ &           18804 &   1170    &     18803   &     192     \\
          &  $3\times 10^{-8}$ &           18836 &    224    &     15256   &      50     \\
          &          $10^{-8}$ &           17060 &     50    &   \nodata   & \nodata     \\
      \hline
      2.5 &  $3\times 10^{-6}$ &           18597 &  19036    &     18597   &     786    \\
          &          $10^{-6}$ &           18609 &   4738    &     18608   &     208    \\
          &  $3\times 10^{-7}$ &           18613 &    954    &     15958   &      53    \\
          &          $10^{-7}$ &           18658 &    203    &   \nodata   & \nodata    \\
          &  $3\times 10^{-8}$ &           14072 &     41    &   \nodata   & \nodata    \\
      \hline                                                
        3 &          $10^{-5}$ &           18354 &  19466    &     18354   &     215    \\
          &  $3\times 10^{-6}$ &           18381 &   4205    &     15973   &      54    \\
          &          $10^{-6}$ &           18449 &    966    &   \nodata   & \nodata    \\
          &  $3\times 10^{-7}$ &           18517 &    174    &   \nodata   & \nodata    \\
          &          $10^{-7}$ &           13714 &     41    &   \nodata   & \nodata    \\
\cutinhead{Galactic and Isotropic Diffuse Background\tablenotemark{(b)}}
      1.5 &  $2.3\times 10^{-8}$ &           90741 &     63    &   \nodata   & \nodata     \\
        2 &  $1.2\times 10^{-7}$ &           92161 &     60    &   \nodata   & \nodata     \\
      2.5 &  $4.5\times 10^{-7}$ &           86226 &     47    &   \nodata   & \nodata    \\
        3 &  $2.0\times 10^{-6}$ &           94412 &     61    &   \nodata   & \nodata    \\
\enddata

\tablenotetext{(a)}{Integral 100 \mev to 100 \gev flux.}
\tablenotetext{(b)}{
\newtext{For the Galactic simulations, the quoted fluxes are
if it was placed in the galactic center and is scaled by Equation~\ref{scale_flux_by_background}.}
}

\tablecomments{
    A list of the spectral models of the simulated point-like sources
    which were tested for extension.  For each model, the number of
    statistically independent simulations and the average value of \ts is
    also tabulated.  
    \newtext{The top rows are the sources simulated on top of an isotropic background and
    the bottom rows are the simulations on top of the Galactic and isotropic
    background.}
}
\end{deluxetable}

@@

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/plot_tsext_plane_color.eps}
    \else
    \plotone{mc_plots/plot_tsext_plane_bw.eps}
    \fi
    % this plot came from $tsext_plot_plane/tsext_plane_plot.py
    \caption{
    \newtext{
    The same plot as Figure~\ref{ts_ext_mc_1000}, but fitting sources
    simulated on top of the Galactic diffuse and isotropic diffuse
    emission.
    }
    }\label{tsext_plane_plot}
  \end{figure}

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/ts_comparison_w44sim_color.eps}
    \else
    \plotone{mc_plots/ts_comparison_w44sim_bw.eps}
    \fi
    % this plot came from $w44simplots/plot_ts_values.py
    \caption{
    \newtext{The distirbution of \ts values when fitting statistically
    independent simulations of the
    elliptical ring shaped SNR W44. (a) is the distribution of \ts values
    when fitting W44 as a point-like source and (b) is the
    distribution of \tsext when fitting the SNR with a Gaussian and uniform disk 
    spatial model. (c) is the distribution of the change in TS when
    fitting the source with an elliptical disk spatial model compared to
    fitting it with a radially symmetric spatial model and (d) 
    when fitting the source with a elliptical ring spatial model compared
    to an elliptical disk spatial model.
    }
    }\label{ts_comparison_w44sim}
\end{figure}

>>>>

\newtext{
These simulations spanned a large range of fluxes 
for two different energy ranges assuming an isotropic background.
We performed a second simulation to assess any effects that could
be introduces by performing this test in the presence of a highly
structured background.

Our simulation setup was the same as above except that the sources were
simulated on top of and analyzed assuming the presence of the standard
Galactic diffuse and isotropic background models used in 2FGL.  In our
simulations, we selected our sources to have a random position on the sky
such that the absolute value of the galactic latitude of the source was
less than 5\degree. This probes the most structured areas of the galaxy.

To limit the number of tests, we selected only one flux
level for each of the four spectral indices and we perform
this test only in the 1 \gev to 100 \gev energy range. 
The fluxes were selected so that $\ts\sim50$ which is around 
the significance level for which on might
expect to be able to spatially resolve the source. 
We only tested these relatively dim sources because they are most likely
to be affected by the background.

Because the Galactic diffuse emission is highly structure, the point-source
sensitivity can vary significantly across the galactic plane.
To account for this, we scaled the flux (for a given spectral index)
so that the source always has approximately the same signal-to-noise ratio:
\begin{equation}
  \label{scale_flux_by_background}
  F(\vec{x}) = F(\text{GC}) \times \left(
  \frac{B(\vec{x})}{B(\text{GC})}\right)^{1/2}.
\end{equation}
Here, $\vec{x}$ is the position of the simulated source, $F$ is the integral
flux of the source from 100 \mev to 100 \gev, $F(\text{GC})$
is the same quantity if the source were at the galactic center, $B$
is the integral of the Galactic diffuse and isotropic emission
from 1 \gev to 100 \gev and $B(\text{GC})$ is the same quantity
if the source were at the galactic center.  Table~\ref{ts_ext_num_sims}
contains $F(\text{GC})$ and the average value of \ts for the four spectral models.
For each spectrum, we performed $\sim90,000$ simulations.

Figure~\ref{tsext_plane_plot} shows the cumulative density
of \tsext compared to the $\chi^2_1/2$ distribution of
Equation~\ref{ts_ext_distribution}. For small values of \tsext,
there is good agreement between the simulations and
theory.  For the highest values of \tsext, there is possibly
a small discrepancy, but limited statistics makes this hard to quantify.
}

\subsection{Assessing the Bias Due to Incorrect Spatial Models}
\label{bias_wrong_spatial_model}

\newtext{
We performed a Monte Carlo study to asses the bias that is introduced by
incorrectly modeling the spatial structure of an extended source. This
is important because any assumed spatial model is just an approximation
to the true shape of a source.

To assess this systematic, we simulated the spatially extended ring-type SNR W44.
We selected W44 because it is the most significant extended source detected by the LAT 
that has a non-radially symmetric photon-distribution \citep{w44}.

W44 was simulated with a power-law spectral model with an integral flux
of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100
\gev and a spectral index of 2.66.
The flux and spectral index of this source
were taken from our analysis of W44 which is described in Section~\ref{validate_known}.

W44 was simulated with the elliptical ring spatial model described in
\cite{w44}.  Because that publication does not provide the numbers describing
the parameters of the ellipse, we summarize them here for completeness. The 
ellipse has a semi-major axis of 0\fdg3 and a semi-minor axis of 0\fdg19. The
ellipse predicts emission only for the outer 0.75\% of the shape and
the has a position angle of $147\degree$ measured east of celestial north.

We used a simulation setup similar to that described in
Section~\ref{monte_carlo_validation}, but the source was simulated on
top of and analyzed assuming the presence of the standard Galactic diffuse and
isotropic background model used in 2FGL.  This simulation was
in the 1 \gev to 100 \gev energy range and
W44 was simulated over the two-year time range included in the
2FGL catalog. 
In the simulations, we disabled the inherent energy dispersion of photons
by the LAT. The bias caused by ignoring energy dispersion 
will be discussed in an upcoming paper by the LAT collaboration \citep{lat_on_orbit_psf}.
In total, we performed 985 identical simulations.

The simulated sources were fit using a point-like spatial model,
a radially-symmetric uniform Gaussian and disk spatial model, 
an Elliptical disk spatial model, and finally with an Elliptical
ring spatial model.
We obtained the best fit spatial parameters using \pointlike and, using 
these best fit spatial parameters, obtained the best fit spectral parameters 
using \gtlike.

Figure~\ref{ts_comparison_w44sim}a shows the distribution of \ts values when 
fitting the simulations of W44 as as a point-like source.
The sources are very significant ($\ts\sim3500$).
Figure~\ref{ts_comparison_w44sim}b shows the distribution of \tsext values
when fitting the source as a radially-symmetric uniform disk and Gaussian source.
The sources are very significantly extended ($\tsext\sim250$). 
On average \tsext is slightly larger when
fitting the source with the disk spatial model compared to the Gaussian spatial model,
consistent with the fact that the simulated source's true spatial model has a sharp edge.
Figure~\ref{ts_comparison_w44sim}c then shows the change in \ts 
when fitting the simulated source as
an elliptical disk compared to fitting the source as a disk. Since the changes
in \ts are on average $\sim30$, we see that our simulated source is significantly better
described with an elliptical spatial model. Finally, 
Figure~\ref{ts_comparison_w44sim}d shows the changes in \ts when fitting
the sources with an elliptical ring spatial model compared to fitting them
with elliptical disk spatial models.
Since the changes are on average $\sim9$, the simulated sources are only somewhat better described
by the true spatial model.

Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b
show the distributions of best fit flux and spectral indices when fitting
the simulated sources.
When fitting the sources with a point-like
spatial model, there is a $\sim$10\% bias in the fit flux and
a $\sim5\%$ bias in the fit index. When fitting the sources assuming any
of the extended spatial models, there is no bias in the best fit spectral parameters
(within the precision of the Monte Carlo study). The reason is that
within the finite angular precision and limited statistics of the LAT, 
all of the extended spatial models can be adjusted to look very similar.

Figure~\ref{bias_w44sim}c plots the best fit 68\% containment radius.  
For the elliptical ring spatial model, there is no significant bias in the best fit size. 
None of the other spectral models induced a bias greater
than $\sim10\%$. From this, we see that \rsixeight is a reasonable measure of the true 68\%
containment radius for a reasonable spatial models.

For completeness, Figure~\ref{bias_w44sim}d plots the distribution of best
fit elliptical eccentricities and Figure~\ref{bias_w444im}e plots the
distribution of orientation angles
when the sources were fit with elliptical
disk and elliptical ring spatial models.  
The eccentricity is defined as
$\sqrt{1-b^2/a^2}$, where $a$ is the length of the semi-major axis and
$b$ is the length of the semi-minor axis.  
There is no systematic bias in the eccentricities or orientation angles.
Finally, Figure~\ref{bias_w44sim}f shows that the distribution of best fit
ring fractions is unbiased when the sources are fit with the elliptical
ring spatial model.
}

@@

\newtext{
We considered an alternate Bayesian formulation of this test.
We considered the Bayesian information criterion \citep[BIC,][]{BIC_statistical_test},
but found it difficult
to apply to LAT data because it required a term including the number of data points
and for LAT events. Because there are many photons included in an analysis that contribute only
 marginally to the analysis of a source, it is unclear how this test could be applied.
We also considered the Akaike information criterion test \citep[\aic,][]{AIC_statistical_test}.
The \aic is defined as
\begin{equation}
  \aic=2k-2\log\likelihood,
\end{equation}
where $k$ is the number of parameters in the model. 
In this formulation, the best model is considered to be the one that minimizes the \aic.
The first term penalizes models with additional parameters.

Because the two point-like source hypotheses has
three more parameters than the single extended source hypothesis (two spatial
parameters and two spectral parameters compared to one extension parameter),
we note that the $\tsext>\tsinc$ is mathematically equivalent to the test:
\begin{equation}
  \aic_\text{ext} < \aic_\text{2pts} - 6.
\end{equation}
Therefore, our original test has an 
equivalent Bayesian formulation requiring that $\aic_\text{ext}$ 
be sufficiently smaller than $\aic_\text{2pts}$.
}

@@

For each candidate that was not biased by neighboring point-like
sources or by large-scale residuals in the diffuse emission model, we
improved the model of the region by deciding on a case by case basis which
background point-like sources should be kept.  We kept in our model the
sources that we
believed represented physically distinct sources and we removed 
sources that we believed were included in the 2FGL catalog to compensate
for residuals induced by not modeling the extension of the source.
Soft nearby point-like 2FGL sources that were not significant at higher energies
were frozen to the spectras predicted by 2FGL.
When deciding
which background sources to keep and which to remove, we used as much as possible
multiwavelength information about possibly extended source counterparts
to help guide our choice. For each extended source presented in 
Section~\ref{new_ext_srcs_section}, we describe any modifications from 2FGL
of the background model that were performed.
\newtext{In Table~\ref{fake_2fgl_sources}, we will summarize the sources that were 
included in 2FGL to account for residuals induced by not modeling the extension of
nearby extended sources.}

@@

Nine extended sources not included in the 2FGL catalog were found by our
extended source search. Two of these have been previously
studied in dedicated publications: RX\,J1713.7$-$3946 and Vela
Jr. \citep{rx_j1713_lat,vela_jr_lat}.
Two of these sources were
found when using photons with energies between 1 \gev and 100 \gev and seven
were found when using photons with energies between 10 \gev and 100 \gev.
For the sources found at energies above 10 \gev, we restrict our
analysis to higher energies because of the issues
of source confusion and diffuse emission modeling described in
Section~\ref{extended_source_search_method}.
The spectral and spatial properties of these nine sources are summarized
in Table~\ref{new_ext_srcs_table} and the results of our investigation of
systematic errors are presented in Table~\ref{alt_diff_model_results}.
Table~\ref{alt_diff_model_results}
also
compares the likelihood assuming the source is spatially
extended to the likelihood assuming 
that the emission originates from two independent point-like
sources. For these new extended sources, $\tsext>\tsinc$ 
so we conclude that 
the \gev emission does not originate from two physically
distinct point-like sources (see Section~\ref{dual_localization_method}).  
Table~\ref{alt_diff_model_results} also includes the
results of the extension fits using variations of the PSF and the Galactic
diffuse model described in Section~\ref{systematic_errors_on_extension}.
There is good agreement between \tsext and the fit size using the standard
analysis, the alternative approach to modeling the diffuse emission, and the alternative PSF.
This suggests that the sources are robust against mis-modeled features in the diffuse
emission model and uncertainties in the PSF.
\newtext{Finally, in Table~\ref{fake_2fgl_sources} we 
summarize the sources included in 2FGL to account for residuals induced
by not modeling the extension of nearby extended sources.}

@@

2FGL\,J1837.3$-$0700c was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the \tev source HESS\,J1837$-$069.  This source is
in a complicated region.  Figure~\ref{1FGL_J1837.5-0659c}a shows a
smoothed counts map of the region and overlays the \tev contours of
HESS\,J1837$-$069 \citep{hess_plane_survey}.  There are two very nearby
point-like 2FGL sources, 2FGL\,J1836.8$-$0623c and 2FGL\,J1839.3$-$0558c,
that clearly represent distinct sources.  On the other hand, there is
another source 2FGL\,J1835.5$-$0649 located between the three sources that
appears to correlate with the \tev morphology of HESS\,J1837$-$069 but
at \gev energies
does not appear to represent a physically distinct source.  We concluded
that this source was included in the 2FGL catalog to compensate for residuals induced by
not modeling the extension of this source and removed it from our model
of the sky.  Figure~\ref{1FGL_J1837.5-0659c}b shows a
counts map of this region after subtracting these background sources.
After removing 2FGL\,J1835.5$-$0649,
we tested for
source confusion by fitting 
2FGL\,J1837.3$-$0700c
instead as two point-like sources.
\newtext{Because $\tsinc=10.8$ is less than $\tsext=18.5$, we conclude that this emission
does not originate from two nearby point-like sources.}

\newtext{With this model, 2FGL\,J1837.3$-$0700c was found to have an
extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$.}
While fitting the extension of 2FGL\,J1837.3$-$0700c,
we iteratively relocalized the two closest
background sources along with the extension of 2FGL\,J1837.3$-$0700c but
their positions did not significantly change.  2FGL\,J1834.7$-$0705c
moved to $(l,b)=(24\fdg77,0\fdg50)$, 2FGL\,J1836.8$-$0623c moved
to $(l,b)=(25\fdg57,0\fdg32)$.

@@

\startdata
\multicolumn{6}{c}{\newtext{Isotropic Background}} \\
\hline
      1.5 &  $3\times 10^{-7}$ &           18938 &  22233    &     18938   &    8084     \\
          &          $10^{-7}$ &           19079 &   5827    &     19079   &    2258     \\
          &  $3\times 10^{-8}$ &           19303 &   1276    &     19303   &     541     \\
          &          $10^{-8}$ &           19385 &    303    &     19381   &     142     \\
          &  $3\times 10^{-9}$ &           18694 &     62    &     12442   &      43     \\
      \hline
        2 &          $10^{-6}$ &           18760 &  22101    &     18760   &    3033     \\
          &  $3\times 10^{-7}$ &           18775 &   4913    &     18775   &     730     \\
          &          $10^{-7}$ &           18804 &   1170    &     18803   &     192     \\
          &  $3\times 10^{-8}$ &           18836 &    224    &     15256   &      50     \\
          &          $10^{-8}$ &           17060 &     50    &   \nodata   & \nodata     \\
      \hline
      2.5 &  $3\times 10^{-6}$ &           18597 &  19036    &     18597   &     786    \\
          &          $10^{-6}$ &           18609 &   4738    &     18608   &     208    \\
          &  $3\times 10^{-7}$ &           18613 &    954    &     15958   &      53    \\
          &          $10^{-7}$ &           18658 &    203    &   \nodata   & \nodata    \\
          &  $3\times 10^{-8}$ &           14072 &     41    &   \nodata   & \nodata    \\
      \hline                                                
        3 &          $10^{-5}$ &           18354 &  19466    &     18354   &     215    \\
          &  $3\times 10^{-6}$ &           18381 &   4205    &     15973   &      54    \\
          &          $10^{-6}$ &           18449 &    966    &   \nodata   & \nodata    \\
          &  $3\times 10^{-7}$ &           18517 &    174    &   \nodata   & \nodata    \\
          &          $10^{-7}$ &           13714 &     41    &   \nodata   & \nodata    \\
\cutinhead{\newtext{Galactic Diffuse and Isotropic Background\tablenotemark{(b)}}}
      1.5 &  $2.3\times 10^{-8}$ &           90741 &     63    &   \nodata   & \nodata     \\
        2 &  $1.2\times 10^{-7}$ &           92161 &     60    &   \nodata   & \nodata     \\
      2.5 &  $4.5\times 10^{-7}$ &           86226 &     47    &   \nodata   & \nodata    \\
        3 &  $2.0\times 10^{-6}$ &           94412 &     61    &   \nodata   & \nodata    \\
\enddata

\tablenotetext{(a)}{Integral 100 \mev to 100 \gev flux.}
\tablenotetext{(b)}{
\newtext{For the Galactic simulations, the quoted fluxes are
if the sources were placed in the Galactic center and the actual
flux is scaled by Equation~\ref{scale_flux_by_background}.}
}

\tablecomments{
    A list of the spectral models of the simulated point-like sources
    which were tested for extension.  For each model, the number of
    statistically independent simulations and the average value of \ts is
    also tabulated.  
    \newtext{The top rows are the sources simulated on top of an isotropic background and
    the bottom rows are the simulations on top of the Galactic diffuse and isotropic
    background.}
}
\end{deluxetable}

@@

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/plot_tsext_plane_color.eps}
    \else
    \plotone{mc_plots/plot_tsext_plane_bw.eps}
    \fi
    % this plot came from $tsext_plot_plane/tsext_plane_plot.py
    \caption{
    \newtext{
    The same plot as Figure~\ref{ts_ext_mc_1000}, but fitting sources
    simulated on top of the Galactic diffuse and isotropic background.
    }
    }\label{tsext_plane_plot}
  \end{figure}

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/ts_comparison_w44sim_color.eps}
    \else
    \plotone{mc_plots/ts_comparison_w44sim_bw.eps}
    \fi
    % this plot came from $w44simplots/plot_ts_values.py
    \caption{
    \newtext{The distribution of \ts values when fitting statistically
    independent simulations of the
    elliptical ring shaped SNR W44. (a) is the distribution of \ts values
    when fitting W44 as a point-like source and (b) is the
    distribution of \tsext when fitting the SNR with a Gaussian and uniform disk 
    spatial model. (c) is the distribution of the change in TS when
    fitting the source with an elliptical disk spatial model compared to
    fitting it with a radially symmetric spatial model and (d) 
    when fitting the source with a elliptical ring spatial model compared
    to an elliptical disk spatial model.
    }
    }\label{ts_comparison_w44sim}
\end{figure}
